### 2014-02-13 tex/pseudo-code.tex
Added

%\item $n$ are numbers, and the set of all positive natural numbers is $\mathbb{N}^+$.
\begin{itemize}
\item $x \in X$ is a variable
\item $f\in F$ is a field name in an object
\item $r\in V$ is a reference
\item $e$ is an expression.
  \begin{itemize}
  \item $v$
  \item $x$
  \item $(e\ \$\ f)$
  \item $(x\ := e)$
  \item
  \end{itemize} Expressions can be values $v$, sequencing
  ($(begin\ e\ \ldots)$), field access ($(x.f)$ or $(x.f := e)$), and
  other constructs to be defined soon,...
\item $\mu$ is the text that defines classes and methods.
\item $P$ is a program $(\mu, (C m))$ where $C$ is a class defined in
  $\mu$ and $m$ is a method in that class.
\item $(L,R)$ represent the heap and form a bipartite graph (see below).
\item $\eta : X \rightarrow V$ is an environment
\item $k$ is a continuation to resolve evaluation order and return points from calls
\begin{itemize}
\item $\mathtt{end}$: nothing comes next
\item $(*\ \$\ f \rightarrow k)$: access field $f$ once expression is reduced to a reference.
\end{itemize}
\item $s = (\mu\ h\ \eta\ e\ k)$ is a machine state.
\item $(\mu\ h^\prime\ \eta^\prime\ e^\prime\ k^\prime) =
  \mathrm{execute}(\mu, h, \eta, e, k)$ is a function that returns a
  state by evaluating the expression.
\end{itemize}

The heap is a bipartite graph defined on locations $L$ and references
$R$. $R$ and $L$ include the special symbol $\bot$ to indicate an
uninitialized reference and location respectively. Additionally, $L$
includes a special location $\mathtt{NULL}$ for null references.

@@

The heap is now defined
as $h = (L\ R\ \mathit{ref}\ \mathit{loc})$ where
\begin{itemize}
\item $\mathit{ref} : L \times F \mapsto R$ is the
  connection between locations and references on a named field. The
  function can also be viewed as a set $\mathit{ref} \subseteq L
  \times F \times R$ in a set if that is preferred to a function.
\item $\mathit{loc} : R \mapsto 2^{L \times \Phi}$ is the connection
  between a reference and a location on a constraint. The function
  $\mathit{loc}$ can also be viewed as a set $\mathit{loc} \subseteq R
  \times \Phi \times L$.
\end{itemize}

>>>>

%\item $n$ are numbers, and the set of all positive natural numbers is $\mathbb{N}^+$.
This paper uses a standard definition of constraints $\phi \in \Phi$
assuming all the usual relational operators and connectives. The heap
is a labeled bipartite graph consisting of references $R$ and
locations $L$ in the store. The functions $R$ and $L$ are defined for convenience
in manipulating the labeled bipartite graph.
\begin{itemize}
\item $R(l,f)$ maps location-field pairs from the store to a reference in $R$; and
\item $L(r)$ maps references to a set of location-constraint pairs in the store.
\end{itemize}
A reference is a node that gathers the possible store locations for an
object during symbolic execution. Each store location is guarded by a
constraint derived from the path constraint in the symbolic execution.
Intuitively, the reference is a level of indirection between a
variable and the store, and the reference is used to group a set of
possible store locations each predicated on the associated constraint.
For an variable (or field) to access any particular store location associated with its reference, the corresponding constraint must be satisfied.

\begin{comment}
 defined on value sets $L$ and references
$R$. $R$ and $L$ include the special symbol $\bot$ to indicate an
uninitialized reference and location respectively. Additionally, $L$
includes a special location $\mathtt{NULL}$ for null references.
\end{comment}

@@
